404 -- Page Not Found   

### 2025-09-04 LipidProbe/PhosphatidicAcid.qmd
Working to address reviewer concerns

:::{.border}
::: {layout="[[-15,85], [100]]"}
![(A) Native Phosphatidic Acid.](/LipidProbe/Structures/PA.png)

@@

::::{.callout-tip}
### Cell background: HeLa

@@

:::::{.border}
::::{#fig-PE_GOplots}
::: {.panel-tabset}

>>>>

::: {.border}
::: {layout="[[-15,85], [100]]"}
![(A) Native Phosphatidic Acid.](/LipidProbe/Structures/PA.png)

@@

:::: {.callout-tip}

### Cell background: HeLa

@@

:::::{.border}
::::{#fig-PA_GOplots}
::: {.panel-tabset}

### 2025-09-04 LipidProbe/Sphingosine.qmd
Working to address reviewer concerns

:::{.cells collapse="true"}
::::{.cells-header}
Cell background: Huh7
::::
::::{.cells-container}

@@

::::
:::

:::{.cells collapse="true"}
::::{.cells-header}
Cell background: HeLa
::::
::::{.cells-container}

@@

**\*Data presentation still in development.**

::::
:::

>>>>

:::{.callout-warning collapse="false"}
### Cell Background: Huh7

@@

<!-- End of .callout-warning block -->
:::

:::{.callout-warning collapse="false"}

### Cell Background: HeLa

@@

**\*PSM data presentation still in development.**

See [Höglinger et al. 2017](https://lipidinteractome.org/individualstudies/dh_2017) for results in context with Diacylglycerol and 8-3 Fatty Acid data.

<!-- End of .callout-warning block -->
:::

### 2025-09-04 StudyInformation_includes/RM_2021_include.qmd
Working to address reviewer concerns

Label free quantification *(as reported here, enabled via fresh analysis by Frank Stein, EMBL)*

@@

>>>>

Label free quantification *(as reported here, enabled via fresh analysis by Frank Stein, EMBL -- details below)*

@@

#### Data analysis

**The authors of this paper were unable to provide the original results of their dataset, and we applied a label-free quantification data pipeline to their mass spectrometry files, publicly-available on ProteomExchange**

For this analysis, raw protein intensities were processed by first selecting unique proteins supported by at least two razor peptides. Batch effects were then removed, and missing values were imputed using a hybrid strategy: KNN imputation was applied to high-confidence proteins with replicate-level missingness, while low-confidence proteins were assigned minimum detected values (MinDet). The data were subsequently variance-stabilized and normalized, after which differential abundance testing was performed using the limma framework. Parallel analyses were also carried out with the fdrtool package, with significance thresholds defined consistently across methods. Proteins were classified according to standard criteria: hits (FDR < 0.05 and |fold-change| > 1.5), candidates (FDR < 0.2 and |fold-change| > 1.5), enriched candidates (FDR < 0.2 and fold-change > 1.5), enriched hits (FDR < 0.05 and fold-change > 1.5), and all others as non-significant.
